---
title: 'Prepare Data'
author: 
output: 
  github_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r "setup", include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center",
                      fig.path=('../../report/figures/'))
library(printr)
options(digits = 2)
library(rmarkdown)
```

# Scripts
- [Required Packages &amp; Reproducibility](#required-packages-&amp;-reproducibility)
- [Tidy Data](#tidy-data)
- [Save Data for Analysis](#save-data-for-analysis)
- [Check Missing Values](#check-missing-values)
- [Visualization of Data](#visualization-of-data)
  - [Dependent Variable](#dependent-variable)
  - [Treatment Conditions](#treatment-conditions)
  - [Correlations Matrix](#correlations-matrix)

## Required Packages &amp; Reproducibility
```{r "env", message=FALSE, warning=F, results='hide'}
rm(list=ls())
source(here::here("src/lib/functions.R"))
renv::snapshot()
```

## Tidy Data
This code chuck downloads the data from Qualtrics using the API and cleans the raw data.

```{r "get data from Qualtrics", results="hide"}
d <- fetch_survey(surveyID = "SV_7PoXOEVMUF1JZn8", 
                    verbose = TRUE, force_request = T,
                    label = FALSE, convert = FALSE)
source(here("src/data-processing/clean_data.R"))
```

## Save Data for Analysis
```{r "save data",eval=FALSE}
save(d, file = here("data/intermediate/cleaned_data.RData"))
```

## Visualization of Data

### Dependent Variable
```{r "Dependent Variable", echo=F, fig.width=10, fig.height=8}
d %>%
  select(POST_2, POST_3, POST_4) %>%
  pivot_longer(cols = POST_2:POST_4,
               names_to = "dvs") %>%
  mutate(dvs = recode(dvs,
                       POST_2 = "Item 2",
                       POST_3 = "Item 3",
                       POST_4 = "Item 4"),
         value = as.numeric(value)) %>%
  group_by(dvs) %>%
  summarise(means = mean(value, na.rm=T),
            stdev = sd(value, na.rm=T)) %>%
  mutate(lower = means - (1.56 * stdev),
         upper = means + (1.56 * stdev)) %>% 
  ggplot(aes(x = dvs, y = means,
             ymin = lower, ymax = upper)) +
  geom_point(position = position_dodge(.5)) + 
  geom_errorbar(position = position_dodge(.5), width = 0) +
  labs(y = "1 (Strongly disagree) - 5 (Strongly Agree)", 
       x = "") +
  theme_minimal() +
  scale_color_manual(values = fig_cols) +
  coord_flip() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="none",
        legend.title = element_blank()) 
```

### Treatment Conditions
```{r "Independent Variables", echo=F, message=FALSE, warning=FALSE,fig.width=10, fig.height=10}
d %>%
  select(populism) %>%
  mutate(populism = recode(populism, 
                           `Burgers` = "Civic Conception", 
                           `Volk` = "Ethnic Conception")) %>%
  group_by(populism) %>%
  summarise(n = n()) %>%
  mutate(perc = round(n/sum(n),2),
         perc2 = paste0(perc*100, "%")) %>%
  ggplot(aes(x = perc, y = populism, label = perc2)) +
  geom_col(width=0.75) + 
  geom_text(position = position_fill(vjust=0.25), color = "white", fontface = "bold") +
  labs(y = "", x = "", title = "Distribution of Treatments") +
  scale_x_continuous(labels=scales::percent) +
  theme_minimal() +
  scale_fill_manual(values = fig_cols) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="bottom",
        legend.title = element_blank()) +
  guides(fill=guide_legend(ncol=4,byrow=TRUE))
```


### Correlations Matrix
```{r "Correlations Matrix", eval = F, echo=F, message=T, warning=T, fig.width=15, fig.height=15}
d %>%
  select(`Gender` = F1,
         `Age` = F2,
         `Education` = F9,
         `Region`  = F3,
         `Urbanness`  = F4,
         `Migration Background`  = F5,
         `Job`  = F7,
         `Income`  = F8,
         `Position: Immigration (%)`  = PreT1,
         `Position: Immigration`  = PreT2,
         `Position: Defense`  = PreT3,
         `Position: Education`  = PreT4,
         `Position: Attitude Women in Politics`  = PreT5,
         `Ideology`  = PreT6,
         `Political Efficacy` = PreT7, 
         `Position: COVID-19 Policy` = PreT8,
         `DV: Trait Evaluation` = PT1,
         `DV: Favorability` = PT2,
         `DV: Representation` = PT3,
         `DV: Career Prospects` = PT4) %>%
  ggcorrmat(
  type = "robust", # correlation method
  cor.vars = c(everything()), # a range of variables can be selected
  colors = c(fig_cols[1], fig_cols[4], fig_cols[8]),
  title = "Correlalogram for Variables under Study"
)
```
